dispRity manual

### 2017-11-08 inst/gitbook/index.Rmd
Note for figshare doi for manual
gitbook update

<!-- badges out start -->
[![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=release)](https://travis-ci.org/TGuillerme/dispRity)
[![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/release/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges out end   -->

@@

Note that this citation is only temporary (but can still be used!).
A future proper version of the latest package release, this manual and an associated methods paper should be submitted soon(ish!).

>>>>

<!-- badges out start -->
[![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=release)](https://travis-ci.org/TGuillerme/dispRity)
[![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/master/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges out end   -->

@@

<!-- > Guillerme, T. & Cooper, N. (2016). The dispRity R package manual. Fighsare XXXX -->

Note that this citation is only temporary (but can still be used!).
A proper description of the package is currently in review in Methods in Ecology and Evolution and should be re-submitted this winter.
Upon acceptance (hopefully!), a proper DOI will be released for this manual and the package description.
